Time Series Length at Which Block Bootstrapping is Effective for Estimation of Variance

### 2022-09-14 Manuscript/manuscript.tex
Update

For the simulations using a constant block length of 10, the sample size was gradually lowered by increments of 20 to see when
the block bootstrap would begin to consistently return coverage rates below .90. For AR = 0.2 using a constant l, results for
sample sizes ranging from 400 to 20 were observed. For AR = 0.4 using a constant l, results for sample sizes ranging from 600
to 20 were observed. For AR = 0.6, using a constant l, results for sample sizes ranging from 900 to 220 were observed. For the simulations in which the block length was the square root of the time series length, the only sample sizes used were perfect squares so that the blocks would have whole number lengths. For AR = 0.2 using l = sqrt{n}, results for sample sizes ranging from 625 to 36 were observed. For AR = 0.4 using sqrt{n}, results for sample sizes ranging from 900 to 121 were observed. For AR = 0.6 using l = sqrt{n}, results for sample sizes ranging from 1600 to 121 were observed.

@@

As the AR Coefficient increases, it was found unsurprisingly that a larger sample size was required for effective block bootstrap estimation.

>>>>

For the simulations using a constant block length of 10, the sample size was gradually lowered by increments of 20 to see when
the block bootstrap would begin to consistently return low coverage rates. For AR = 0.2 using a constant l, results for
sample sizes ranging from 400 to 20 were observed. For AR = 0.4 using a constant l, results for sample sizes ranging from 600
to 20 were observed. For AR = 0.6, using a constant l, results for sample sizes ranging from 900 to 220 were observed. For the simulations in which the block length was the square root of the time series length, the only sample sizes used were perfect squares so that the blocks would have whole number lengths. For AR = 0.2 using l = sqrt{n}, results for sample sizes ranging from 625 to 36 were observed. For AR = 0.4 using sqrt{n}, results for sample sizes ranging from 900 to 121 were observed. For AR = 0.6 using l = sqrt{n}, results for sample sizes ranging from 1600 to 121 were observed.

@@

As the AR Coefficient increases, it was found unsurprisingly that a larger sample size was required for effective block bootstrap estimation. With l = sqrt{n} and AR = 0.2, all observed coverage rates are lower than .92 for n <= 225. For all n's <= 100, all observed coverage rates were below .90. With l = sqrt{n} and AR = 0.4, all observed coverage rates were below .92 for n <= 441. For all n's <= 144, all observed coverage rates were below .90. With l = sqrt{n} and AR = 0.6, all observed coverage rates were below .92 for n <= 400. For all n's <= 196, all observed coverage rates were below .90.

With a constant l and AR = 0.2, for n <= 180, all observed coverage rates were below .92. For all n's <= 60, all observed coverage rates were below .90. With a constant l and AR = 0.4, for n <= 160, all observed coverage rates were below .91. For all n's <= 80, all observed coverage rates were below .90. With a constant l and AR = 0.6, for n <= 380, all observed coverage rates were below .92. For all n's <= 240, all observed coverage rates were below .90.
